---
title: "Vignette Title"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Disclaimer: this package is still at an experimental level, and should only be used for testing, bug reports, and enhancement requests. 

This package has only been tested on these platforms for now, so it might not work on other : 

- neo4j 3.4.0

+ Linux Mint

- neo4j 3.3.3

+ Mac OSX

# rmd4j

The goal of {rmd4j} is to provide a knitr engine for running Neo4J inside an RMarkdown

## Installation

You can install rmd4j from GitHub with:

```{r gh-installation, eval = FALSE}
# install.packages("remotes")
remotes::install_github("ThinkR-open/rmd4j")
```

## Before using 

You need to have downloaded the neo4j [community edition](https://neo4j.com/download/other-releases/), and have unpacked it. 

In order to use this knitr engine, you must have a running connection to a Neo4J server, launched with `$NEO4J_HOME/bin/neo4j start` ($NEO4J_HOME being the folder you've unpacked neo4j into).

## Example

You can start a new document by take using the RMarkdown templates which come with the configuration chunk. 

If you want to add a Neo4J engine to an existing Rmarkdown, add the `set_neo4j_engine` function inside the `setup` chunk in your RMarkdown. 

If you follow the advices below about username and password, this should only be : 

```{r, eval = FALSE}
rmd4j::set_neo4j_engine(cypher_bin = "/Users/colin/soft/graphs/n4j/bin/cypher-shell")
```

_Note: if you're a windows user, you need to specify the file extension (should be .bat)_ 

But with more customisation:

```{r, eval = FALSE}
rmd4j::set_neo4j_engine(cypher_bin = "/Users/colin/soft/graphs/n4j/bin/cypher-shell", 
                        neo4j_user = "colin", 
                        neo4j_passwd = "pouetpouet", 
                        neo4j_adress = "bolt://localhost:7687")
```

You can set: 

+ `cypher_bin` the path to your cypher-shell bin
+ `neo4j_user` your Neo4J username
+ `neo4j_passwd` your Neo4J username
+ `neo4j_format` the format of the output (either auto, verbose, or plain, default is "plain")
+ `neo4j_adress` the url of the cluster, default is "bolt://localhost:7687"

As this chunk might contain some sensible information (like you password), don't forget to `{r setup, include=FALSE}` this chunk. 

## The chunks 

Neo4J chunks should start with a ````{neo4j}`. 

You can run several Neo4J calls in the same chunk. 

## About passwords and username

If you don't specify any `neo4j_user` and `neo4j_passwd`, `set_neo4J_engine()` will not use the `--user` and `--password` args of the cypher-shell. In that case, you'll need to have provided Neo4J your user name and password, or have disabled the password request (see below). 

We strongly recommand to provide your Neo4J password outside of the rmd, as it will prevent any unwanted share of these credentials. 

### Disable Neo4J password request 

Go to `$NEO4J_HOME/conf/neo4j.conf` and uncomment the line : `dbms.security.auth_enabled=true`


### Create aliases (recommanded)

Add to your bash profile: 

```
export NEO4J_USERNAME='yourusername'
export NEO4J_PASSWORD='yourpassword'
```

Via : [Neo4J Knowledge base](https://neo4j.com/developer/kb/how-do-i-authenticate-with-cypher-shell-without-specifying-the-username-and-password-on-the-command-line/)

## Output 

You can mix any other content (including R, of course), inside your Rmarkdown. 

## Example 

### Using github_document as output : 

From [Rmd](https://github.com/ColinFay/neo4Jplayground/blob/master/colintracks.Rmd) to [md](https://github.com/ColinFay/neo4Jplayground/blob/master/colintracks.md). 

## Contact

Questions and feedbacks [welcome](mailto:colin@thinkr.fr)!

You want to contribute ? Open a [PR](https://github.com/thinkr/rmd4j/pulls) :) If you encounter a bug or want to suggest an enhancement, please [open an issue](https://github.com/thinkr/rmd4j/issues).
